\section{Discussion \& Threats to Validity}

\subsection{Optimizing Runtime Throughput}

Several parts of the workflow can limit throughput, particularly test generation, minimization, and sorting. More efficient minimization and sorting algorithms could reduce this overhead. For example, minimization could use a divide-and-conquer strategy that first attempts to remove groups of HTML nodes or CSS declarations, then progressively tests smaller groups when necessary. Unlike the current element-by-element and declaration-by-declaration approach, this could reduce the number of browser executions required to find a compact subject. 

Finally, generation, minimization, and sorting can be parallelized across multiple browser instances or machines. Candidate bugs could be queued for minimization and sorting while other workers continue generating and executing new tests. This would increase throughput, although it introduces resource-management, synchronization, and duplicate-reporting challenges. 

Despite these throughput limitations, the current workflow remains effective because it successfully generates, detects, minimizes, and organizes reproducible browser-layout bugs.

\subsection{Supporting Other Browsers}

Supporting a browser requires a browser-specific configuration, a compatible automation driver, and validation that the browser exposes layout information consistently enough for the test oracle. These requirements make it straightforward to support widely used browsers with robust WebDriver implementations, but they limit practical testing of uncommon browsers and older browser versions.

Less frequently tested browsers may contain defects that are not found by testing dominant browser engines. Supporting these browsers could therefore reveal bugs in engines that receive less testing and maintenance. However, support for additional browsers has diminishing returns because most web users are concentrated in a small number of major browser engines. 

The supported Chromium, WebKit/Safari, and Firefox configurations cover most
browser usage.  Worldwide in May 2026, Chrome accounted for 70.25\% of browser
usage, Safari for 15.72\%, and Firefox for 5.14\%; together, these browsers
account for 91.11\% of usage~\cite{statcounterBrowserShare2026}. This leaves
only 8.89\% of usage outside of the main target of \toolname.

Nevertheless, the current implementation remains effective because it supports major browser engines with mature automation tooling and substantial user populations.

\subsection{Increasing Bug Rate}

The bug detection rate directly affects the efficiency of the tool, since a higher rate produces more candidate bugs per executed test case. However, repeatedly finding the same underlying defect is less useful than discovering distinct bugs. Nevertheless, the tool remains effective because sorting and grouping reduce duplicate reports and help distinguish recurring bug patterns.

One approach to increasing the bug rate is to identify a stronger static style-weight configuration before a testing run begins. Results from earlier runs can identify HTML structures, CSS properties, and style updates that have produced layout inconsistencies most often. These observations can then be used to assign greater initial weights to promising properties while preserving lower probabilities for less frequently selected properties.

Separately, a feedback-driven system could dynamically adjust style-selection probabilities while a testing run is running. It could increase the weights of properties associated with novel layout discrepancies and reduce the weights of configurations that repeatedly produce uninteresting or duplicate results. The system should retain a degree of random exploration so that it does not become overly focused on known bug patterns. Despite this, the current random generation strategy remains useful because it can discover unexpected bug classes without requiring prior knowledge of effective configurations.
