\section{EVALUATION}

(what are the concrete experiments that we want to run? Add in modified
and base styles? For example for the minimization, initial vs final.
Minimization with vs without the move modified styles to base styles.)

\textbf{Q1: How effective is the system at discovering
under-invalidation bugs?}
Main Goal: How effective at triggering a bug? (Success rate; bugs per
number of generation.) Test: Run the system for a fixed number of
iterations and measure how many bugs are found. Variance: display
property, grid property, pixel vs percentage, transform property,
flow-root property, etc.

\vspace{0.5em}

\textbf{Q2: How effective are the minimization and clustering
techniques?}
Main Goal: How effective at processing a bug? (Speed; number of
iterations; time to minimize; time to cluster.) Test: Run the system for
a fixed number of time units and measure how many bugs are found.
Variance: with vs without clustering; with vs without minimization; with
vs without moving modified styles to base styles.

\vspace{0.5em}

\textbf{Q3: Does the system discover real and unique
under-invalidation bugs?}
Main Goal: How effective at finding unique bugs? (Quality; number of
unique bugs; number of duplicate bugs.) Test: Run the system for a long
time and manually measure how many unique bugs are found. Variance: ???

\vspace{0.5em}

\textbf{Benchmarks:}

\vspace{0.5em}

\textbf{Experiment Setup \& Infrastructure:}

\vspace{0.5em}

\textbf{Post-processing Results:}

\vspace{0.5em}

\subsection{Q1: How effective is the system at discovering under-invalidation bugs?}
\textbf{Outcomes:}

\vspace{0.5em}

\subsection{Q2: How effective are the minimization and clustering techniques?}
\textbf{Outcomes:}

\vspace{0.5em}

\subsection{Q3: Does the system discover real and unique under-invalidation bugs?}
\textbf{Outcomes:}

\vspace{0.5em}

\textbf{Case Study 1:}

\vspace{0.5em}

\textbf{Case Study 2:}

\vspace{0.5em}

\textbf{Case Study 3:}

\vspace{0.5em}

\textbf{Developer Responses:}
