\section{Conclusion}
In this paper, we introduced \toolname, a fuzzer designed to expose the undertest bug of under-invalidation bugs in modern browser layout engines. There are no current fuzzers that use self-differential testing to expose this specific bug. Other fuzzers use cross-browser and cross-version comparisons which rely on the notion that there is a correct implementation. Instead compares a browser’s incremental layout against its own from-scratch layout provides a clean and practical oracle for detecting stale layout state after style updates.

\toolname combines this oracle with grammar-directed generation, large DOM and CSS test cases, automated minimization, and clustering. Together, these components allow \toolname not only to find layout bugs, but also to reduce the complexity of the test cases that developers must inspect. Our evaluation shows that \toolname can reproduce known under-invalidation bugs, test hundreds of candidates per minute in Chrome and Firefox, and substantially reduce review volume through minimization and clustering. Most importantly, \toolname found \textbf{15 novel bugs} that were accepted by browser developers, with 7 fixed.

These results show that under-invalidation bugs are a valuable target for browser fuzzing and that self-differential testing is an effective way to expose them making \textbf{\toolname the first fuzzer specifically designed to find browser layout under-invalidation bugs using self-differential testing:}. As browser layout engines continue to evolve and implement increasingly complex features, tools like \toolname can help developers catch subtle correctness bugs earlier and improve the reliability of the web platform.
In addition, we look forward to applying these techniques to other systems that rely on invalidation, including GUI frameworks, spreadsheet calculation pipelines, and incremental build tools.
