\section{IMPLEMENTATION}

\toolname is implemented in Python as an end-to-end, feedback-free fuzzing
pipeline for browser layout invalidation.  The implementation separates a
test case from its serialization, executes the serialized page in a real
browser through Selenium WebDriver. A \UnderInvalidation failure is identified
when there is a discrepancy between incremental and fresh layout computations.
The same pipeline then classifies, minimizes,and sorts the result. 
At a high level, a run has six stages: (1) configuration and browser
selection, (2) generation of a DOM and two style states, (3) execution of
the layout oracle, (4) minimization of a bug-triggering test case, (5) optional
structural grouping and minimization skipping, and (6) report and metric
production.  The following sections describe these stages and the concrete
artifacts exchanged between them.

\begin{figure*}[t]
    \centering
    \resizebox{\textwidth}{!}{%
    \begin{tikzpicture}[
        >=stealth,
        stage/.style={draw, rounded corners=2pt, align=center, minimum height=1.25cm,
            text width=2.9cm, font=\scriptsize, fill=blue!5},
        process/.style={draw, rounded corners=2pt, align=center, minimum height=1.25cm,
            text width=3.1cm, font=\scriptsize, fill=green!7},
        decision/.style={draw, diamond, aspect=1.45, align=center, inner sep=1pt,
            font=\scriptsize, fill=orange!12},
        output/.style={draw, rounded corners=2pt, align=center, minimum height=1.1cm,
            text width=3.0cm, font=\scriptsize, fill=gray!12},
        flow/.style={->, thick},
        optional/.style={->, thick, dashed}
    ]
        \node[stage] (config) at (0,0) {\textbf{1. Configure}\\JSON paths, CSS weights, target browser, limits};
        \node[stage] (generate) at (4,0) {\textbf{2. Generate subject}\\DOM tree + base styles + modified styles};
        \node[stage] (oracle) at (8,0) {\textbf{3. Serialize and execute Oracle}\\incremental layout versus fresh layout computation};
        \node[decision] (bug) at (12,0) {Dimension\\mismatch?};

        \node[output] (pass) at (16,-1.6) {Pass: update counters};
        \node[process] (sort) at (12,-3.2) {\textbf{4. Match existing group}\\Compare the candidate against group rules};
        \node[process] (minify) at (7.6,-3.2) {\textbf{5. Minimize unmatched candidate}\\Retain only oracle-preserving DOM and CSS changes};
        \node[output] (report) at (3.3,-3.2) {\textbf{6. Persist report}\\HTML reproducers, pickled subjects, metadata, variants, and run summary};

        \draw[flow] (config) -- (generate);
        \draw[flow] (generate) -- (oracle);
        \draw[flow] (oracle) -- (bug);
        \draw[optional] (bug.east) -- ++(0.75,0) |- node[near start, above, font=\scriptsize] {No} (pass.west);
        \draw[optional] (pass.north) -- ++(0,2.2) -| (generate.north);
        \draw[flow] (bug.south) -- node[right, font=\scriptsize] {Yes} (sort.north);
        \draw[flow] (sort) -- node[above, font=\scriptsize] {No Match} (minify);
        \draw[optional] (sort.south) -- node[right, align=left, font=\scriptsize] {Match:\\Save in Group} ++(0,-1.05) -| (report.south);
        \draw[flow] (minify) -- (report);
        \draw[optional] (report.north) to[out=105,in=245] node[left, font=\scriptsize] {next test} (generate.south);
    \end{tikzpicture}
    }
    \caption{\toolname pipeline.  Each generated subject is tested by a
    browser-resident layout oracle.  Passing subjects advance the fuzzing
    loop; candidates are structurally classified, minimized when necessary,
    and persisted with their reproduction artifacts and cumulative metrics.}
    \label{fig:implementation-pipeline}
\end{figure*}

\subsection{Configuration, Execution Model, and Test Subjects}

The command-line runner accepts a JSON configuration file and initializes a
process-wide configuration object before any pages are generated.  The
configuration supplies two paths: a directory for persistent bug reports and
a directory for temporary generated pages.  It also supplies a list of
browser variants and a map from CSS property names to generation weights.
The runner supports a bug limit, test limit, and crash limit.  The bug limit
stops the experiment when it reaches the specified cumulative number of bug
reports, while the test limit stops it at the specified cumulative number of
executed test cases.  The crash limit stops the current process after the
specified number of browser or WebDriver failures; crashes from an earlier
resumed process remain in the reported total but do not consume the new
process's allowance.  The \texttt{--no-sort} option disables structural
classification and grouping, causing each candidate to be fully minimized
and saved as an individual report rather than compared with existing bug
groups.  With no explicit limit, the runner remains active until it is
interrupted or the crash limit is reached.

A browser variant specifies a browser type together with its WebDriver path,
viewport, and optional browser settings.  After reading a variant from the
configuration, \toolname builds the corresponding Selenium WebDriver for
Chrome, Firefox, or Safari.  The variant marked \texttt{target} is used for
the main fuzzing loop.
Internally, each generated test is represented as a \texttt{RunSubject}:

\begin{itemize}
    \item an \texttt{ElementTree}, which is a nested representation of the
    generated DOM;
    \item a base \texttt{StyleMap}, containing declarations applied in the
    initial document; and
    \item a modified \texttt{StyleMap}, containing declarations installed
    later by JavaScript.
\end{itemize}

Both style maps are indexed by generated element identifier and then by CSS
property name.  Keeping base and modified declarations separate captures the
state transition being tested: the initial layout is computed from the base
map, and the incremental update is the modified map. 

\subsection{DOM and CSS Generation}

\toolname generates a body subtree recursively.  The current generator uses
\texttt{div} elements and text nodes.  Each \texttt{div} receives a unique
alphabetic identifier derived from a UUID so that it can be addressed from
both CSS and the generated JavaScript.  Generation is probabilistic: the
body is very likely to receive children, while nested \texttt{div}s have a
smaller probability of receiving one or more children.  Text nodes contain
one or more generated sentences, optionally separated by a newline.  This
produces trees with both nested boxes and text-dependent sizing behavior.

For every non-text element, the generator independently constructs base and
modified style maps.  It walks a repository-maintained catalogue of CSS
properties and their supported value generators.  The configured weight is
first constrained to the range 0--100 and then divided by 100 to obtain the
probability of selecting that property, i.e., $P(\text{select}) = w/100$.
Thus, a weight of zero disables the property, a weight of 40 selects it with
probability 0.40, and a weight of 100 selects it whenever it is considered.
This random decision is made independently for each non-text element and for
each of its base and modified style maps.  If selected, a property-specific
generator produces a valid length or keyword value.  Unspecified properties
use a default selection weight, allowing an experiment to focus on selected
properties without having to enumerate the entire catalogue.

This design makes property weighting an input-distribution control rather
than a change to the oracle.  A configuration can emphasize properties that
are relevant to a particular layout behavior while reducing or disabling the
selection of less relevant properties.  The weighted and unweighted
experiments in Section~V therefore execute the same generation and oracle
pipeline but sample different style distributions.

\subsection{Page Serialization and the Layout Oracle}

Each \texttt{RunSubject} is serialized into a self-contained temporary HTML
file.  The serializer recursively emits the element tree, places base
declarations in each element's inline \texttt{style} attribute, and emits a
JavaScript \texttt{makeStyleChanges()} function.  That function assigns every
declaration in the modified style map through the element's \texttt{style}
object.  The generated page also includes a small JavaScript support file
that implements the geometry collection and comparison operations.  The
runner uses a temporary HTML file to execute each generated test case.

The oracle compares two executions that should have final
markup and style declarations an incremental and a fresh layout computation:

\begin{enumerate}
    \item Selenium navigates the target browser to the generated local file
    URL and waits for the document body to be present.
    \item \texttt{makeStyleChanges()} applies the modified declarations to
    the live document.  This is the incremental path whose invalidation
    behavior is under test.
    \item The page records \texttt{getBoundingClientRect()} for every DOM
    element.  Each observation includes the element identifier, tag name,
    and its dimensions.
    \item The page assigns the document element's \texttt{innerHTML}
    property to itself.  This reconstruct forces the the browser to establish a fresh layout for that final state again.
    \item The page collects the dimensions again and compares the two sets.
    A difference in \texttt{x}, \texttt{y}, \texttt{left}, \texttt{right},
    \texttt{top}, \texttt{bottom}, \texttt{width}, or \texttt{height} for
    the same element is returned to Python.
\end{enumerate}

The browser-side comparison returns a list of differing elements.  Each
entry identifies the affected element and records the attributes that differ
as well as the values after incremental application and after document
reconstruction.  An empty list is a pass; a nonempty list is represented as
a layout-bug result.  WebDriver failures produce a separate page-crash
result, while a page-load timeout is reported by the harness.  Recording the
individual geometric fields is useful during triage because it distinguishes,
for example, a stale width from a descendant-position mismatch.

The oracle detects a candidate failure when the incremental and reconstructed
layout paths produce different element dimensions in the selected browser and
viewport. 

\subsection{Fuzzing Loop and Safe Repository}

The runner first constructs a small repository of known-safe subjects.  It
generates and executes subjects until the configured safe directory contains
25 passing serialized \texttt{RunSubject} objects.  The configured report
directory is a persistent, cumulative bug repository: it contains all saved
reports, groups, safe samples, and the run summary for that configuration.
When a later invocation uses the same directory, it continues the same
repository and aggregates newly discovered reports with the existing ones
rather than creating a separate collection.  These safe samples are used to
prevent the grouping algorithm from accepting a rule that would also match known non-bug inputs.

The main loop then generates one subject, executes the oracle, increments
the pass counter for a clean result, and enters post-processing only for a
candidate.  After every completed test, the runner updates the run summary.
The summary records executed tests, passes, candidate bugs, failures that no
longer reproduce during reduction, reports with no remaining modified style,
crashes, elapsed time, and cumulative minimization and sorting time.  It also
counts standalone reports, grouped reports, and groups by scanning the report
directory. \todo{Not in final version} Threshold snapshots are written at every ten candidates and
every 60 seconds of accumulated runtime, which supports time-series plots.

The runner resumes these cumulative statistics if a report directory already
contains \texttt{run\_summary.json}. Resuming with the same directory retains the
existing bug reports, bug groups, grouping rules, and safe samples.  New
reports are therefore compared with the accumulated repository and can join
an existing group instead of forcing the grouping process to start again.
This makes interrupted long-running experiments continue as one statistical
run, without losing their prior discovery, grouping, or measurement state.

\subsection{Delta Debugging}

Candidate pages are usually much larger than the condition required to
reproduce a mismatch.  \toolname applies delta debugging to reduce a
bug-triggering test case while preserving the oracle result.  For each proposed simplification,
it deep-copies the current subject, executes the candidate in the target
browser, and retains the copy only if the result remains a bug.  Every
accepted reduction becomes the new subject, so later reductions are tested
against the smallest reproducer found so far.  The delta-debugging process
uses the following proposal families in order:

\begin{enumerate}
    \item remove each element, including its associated base and modified
    style entries;
    \item remove every style map for one element at a time;
    \item remove individual base or modified declarations;
    \item move one modified declaration into the base map, thereby testing
    whether that declaration must be an incremental change rather than merely
    being present in the final state;
    \item replace generated length values with \texttt{20px} or
    \texttt{-20px}, preserving only their sign; and
    \item apply readability-oriented transformations, including minimum box
    sizes, background colors, short identifiers, and an optional in-page
    control overlay.
\end{enumerate}

The fourth step, implemented by
\texttt{Minify\_MoveStyleChangesToFirstLoad}, is particularly important for
this bug class.  If moving a declaration to the initial state preserves the
mismatch, it is not necessary for the incremental transition and can be
removed from the set of modified properties.  Conversely, declarations that
cannot be moved identify the state change that is more likely to matter to
invalidation.  The final oracle run is recorded again after all proposal
families have been exhausted.  If
the candidate no longer reproduces, it is counted as a false positive rather
than saved as a confirmed layout report.  A layout mismatch with an empty
modified-style map is also counted separately because it no longer expresses
the intended incremental CSS-change scenario.

\subsection{Structural Grouping and Minimization Skipping}

Full reduction is expensive when many generated subjects trigger a pattern
already represented in the report directory.  With sorting enabled,
\toolname therefore attempts to match a new candidate against existing bug
groups before full minimization.  A subject is converted to a tree in which
each node contains its tag, identifier, base styles, modified styles, and
children; text is represented explicitly.  The first node with modified
styles is used as the start node for a rule because it anchors comparison on
the update of interest.  The rule represents the DOM structure relative to
this anchor: it compares the modified node and its ancestor/descendant structure,
rather than depending on that node's absolute location in the full page tree.
This allows structurally similar update patterns to match even when they
occur in different generated pages.

A group stores a merged representative tree and an extracted JSON rule.  To
form a candidate rule, the implementation merges two trees recursively.
Equal tags, values, and declarations are retained.  Disagreements are
represented by the wildcard value \texttt{diff}.  The resulting rule consists
of an ordered HTML pattern and the common base and modified style
requirements at the start node.  Matching checks both components: the
incoming subject must contain the ordered structural pattern and at least one
matching element must have the required base and modified declarations.
Wildcards permit variation where the merged reports disagree while retaining
the shared structure and update signal.

Before accepting either a match or a new group, the rule is validated against
the safe repository.  Rules with no modified-style requirement or with a trivial
single-element pattern are rejected, and a rule is rejected if it matches
any safe sample.  This is a conservative guard against a broad structural
description that would classify ordinary pages as bug instances.  It does
not prove semantic equivalence, but it makes group promotion depend on both
bug examples and known non-bug examples.

If an incoming candidate matches an existing rule, the runner skips the
full reduction and saves it as another instance under that group.  Otherwise,
it minimizes the candidate first.  The final minimized subject is then
compared against existing groups and against standalone reports.  Matching a
group adds the new instance to that group.  Matching a standalone report
promotes the two reports into a newly created \texttt{bug-group-*} directory
and writes the extracted rule.  After every group update, group artifacts
are recomputed so the merged representative and rule correspond to the
instances currently stored in that directory.  The sorting time is measured
separately and added to the run summary alongside minimization time; this
makes the cost and benefit of grouping measurable in Section~V.

\subsection{Report Layout, Reproduction, and Variant Results}

Each saved report is placed in either a standalone \texttt{bug-*} directory
or a child directory of a \texttt{bug-group-*} directory.  To keep the bug
repository lightweight, the report stores pickled forms of the pre-reduction
and minimized \texttt{RunSubject}, rather than retaining separate HTML
versions of both pages.  These structured artifacts preserve the DOM and
style states needed to rerun reduction or recompute grouping rules.

The accompanying \texttt{data.json} records the save timestamp, bug type,
all styles used, base and modified style names, the geometric differences
returned by the oracle, whether minimization was skipped, the matched rule,
and the time spent sorting and minimizing.  After minimization, the
runner executes each configured browser variant and records browser name,
browser version, operating-system details, viewport, variant description,
and whether that variant also detects the bug.  These fields distinguish the
target run from supplementary checks and make reports usable when browser
versions or command-line flags change.

Together, these artifacts allow a report to be inspected at several levels:
the original input, the minimized browser reproducer, the exact
geometry disagreement, the structured subject used by automated tooling, and
its relationship to a group.  This is the implementation basis for the
throughput, bug-rate, minimization-time, and grouping measurements reported
in the evaluation.
