\section{BACKGROUND, RELATED WORK, AND MOTIVATION}
This section introduces the fundamental topics related to
\toolname: web browsers, under-invalidation bugs, and the
challenges of fuzzing browser layout engines.

\subsection{Web Browsers}

Web browsers are among the most widely used and economically important
software systems. Their engines parse web content, compute style and
layout, execute scripts, and paint pixels to the screen. Common examples
include Chromium's Blink engine~\cite{chromiumBlink}, Mozilla's Gecko
engine~\cite{mozillaGecko}, and Apple's WebKit engine~\cite{webkitEngine}.
Browser engines require large sustained investment; for example, Open
Web Advocacy estimates that Google provides roughly 90\% of Chromium
development funding and invests around \$1 billion annually in the web
platform~\cite{owa2025googleSearchMonopoly}.

Unlike many traditional fuzzing targets, web browsers process highly
structured inputs made up of HTML elements, CSS style rules, and
JavaScript updates. These inputs can exercise DOM parsing, selector
matching, style resolution, layout, and invalidation~\cite{kosaka2018insideBrowserPart3,mdnWebPerformance}.
Effective browser fuzzing therefore requires more than generating valid
syntax: the test cases must be optimized toward the specific class
of bugs being tested~\cite{mozillaFuzzing,ventuzelo2023browserFuzzing,araoz2026webFuzzing}.

After a page has loaded, browsers rarely recompute the entire page for
every change. Instead, they use invalidation logic to decide which parts
of the rendering state are affected by a style update. Correct
invalidation preserves the performance benefits of incremental rendering
while ensuring that the final pixels match the page's current
state~\cite{firefoxPerformanceBestPractices,kosaka2018insideBrowserPart3}.
Over-invalidation recomputes too much and hurts performance, while
under-invalidation recomputes too little and leaves stale layout or
rendering state visible~\cite{mdnWebPerformance,firefoxPerformanceBestPractices,kilpatrick2021layoutng}.

\subsection{Why Fuzzers Fail to Find Under-Invalidation Bugs}

Most browser fuzzers are optimized for bug classes with explicit failure
signals. JavaScript-engine fuzzers such as CodeAlchemist and DIE
generate complex programs to expose crashes and security
vulnerabilities~\cite{han2019codealchemist,park2020die}. Other browser
fuzzers target specialized attack surfaces such as WebGL or WebAssembly,
where crashes, memory corruption, or API errors provide concrete
oracles~\cite{peng2023gleefuzz,draissi2025wemby}. These approaches are
valuable, but they do not directly test whether a layout engine
correctly updates stale rendering state after a style update.

Rendering-engine fuzzers begin to address this issue, but their goals
still differ from detecting under-invalidation. RTFuzz mutates
render-tree state but primarily evaluates robustness defects such as
crashes~\cite{zeng2026rtfuzz}. Differential rendering fuzzers such as
R2Z2, Metamong, and JANUS compare outputs across versions, executions,
or browsers~\cite{song2022r2z2,song2023metamong,zhou2025janus}. These
oracles are useful, but they do not fully solve layout
under-invalidation because cross-version or cross-browser differences
still require determining which result is correct. Layout
under-invalidation therefore needs a more targeted oracle.

\subsection{Why it is Difficult to Isolate Under-Invalidation Bugs?}

Finding an under-invalidation symptom is only the first step. Isolating
the underlying bug is difficult because incremental layout is a
cache-like optimization: the browser attempts to reuse previous layout
results and recompute only the parts affected by a
change~\cite{panchekha2024reusing}. A stale layout result can depend on
a specific DOM tree, style set, mutation, and internal invalidation
decision. If an irrelevant-looking part of the test case is
removed too early, the browser may take a different invalidation path and
the bug may disappear.

The complexity of layout engines also makes bug reports hard to reduce
to their root cause. Prior work observes that correct incremental layout
requires reasoning about when recomputation can safely be
skipped~\cite{liu2023medea}. As a result, many test cases can
expose the same underlying invalidation mistake through different
combinations of elements, CSS properties, and mutations.

These properties make both minimization and deduplication necessary. A
useful bug report should remove unrelated elements, styles, and
mutations while preserving the incremental-vs-fresh
mismatch~\cite{zellerFuzzingBookReducer}. For HTML/CSS tests, reduction
also needs to respect document structure so minimized tests remain valid
and meaningful~\cite{misherghi2006hdd,webkitTestCaseReduction}.

\begin{center}
\fbox{
\begin{minipage}{0.95\linewidth}
\textbf{Motivation: the need for an under-invalidation browser layout
fuzzer.}
Existing browser fuzzers struggle to detect layout under-invalidation
bugs. \toolname addresses this gap by making browser layout
invalidation testable with a targeted oracle, minimization, and
deduplication.
\end{minipage}
}
\end{center}
