\section{Introduction}

\textit{Web browsers} are central to modern computing,
  hosting applications that correspond to
  over \textbf{80\%} of daily work in some organizations%
  ~\cite{montenegro2025workforce}.
Browser makers therefore invest heavily
  in browser correctness,%
  ~\cite{google-project-zero,mozilla-mythos,w3c,whatwg,wpt,interop},
  including through fuzzing~\cite{clusterfuzz},
  which uses a large number of randomly generated inputs
  to identify bugs in the browser.

Browser developers use fuzzers to find both
  security and correctness bugs.
On the security side, fuzzers such as Domato, Grammarinator,
  Fuzzowski, and MFFA~\cite{domato,grammarinator,fuzzowski,mffa}
  detect crashes in parsers, network libraries, and media engines,
  which are both exposed to untrusted input
  and must maximize performance.
On the correctness side, fuzzers such as
  R2Z2~\cite{song2022r2z2}, Janus~\cite{zhou2025janus}
  and Metamong~\cite{song2023metamong}
  use screenshots to detect browser rendering inconsistencies
  between different versions of the same browser,
  or between renderings of the different pages in the same browser,
  that may indicate a regression or rendering bug.
However, all of these approaches struggle to
  precisely identify \emph{under-invalidation bugs},
  a subtle yet critical type of correctness bug
  in browser layout engines.

\emph{Invalidation} refers to the process by which
  the browser updates internal data structures
  in response to style changes~\cite{panchekha2024reusing}.
Since style changes are frequent
  (often every frame, 60 or even 120 times per second,
  in response to animations),
  substantial research has been devoted
  to designing efficient invalidation procedures%
  ~\cite{megatron,liu2023medea}.
Generally, browsers attempt to update \emph{as little}
  of their internal data structures as possible;
  however, updating \emph{too little} of this internal state
  leads to an incorrect rendering that mixes
  fresh (updated) and stale (not updated) data.
Updating exactly the right set of fields requires
  reasoning about transitive dependencies between layout algorithms,
  reasoning that is difficult enough that public bug trackers
  for Chrome, Firefox, and Safari's layout engines
  contain numerous under-invalidation bugs%
  ~\cite{chromium497183437,chromium379886422,mozilla1452426,mozilla539356,webkit233421,webkit97801}.
Modern invalidation algorithms like LayoutNG~\cite{kilpatrick2021layoutng}
  are purposefully designed to reduce the risk of under-invalidation,
  while some promising algorithms~\cite{mozilla2006reflow}
  have failed precisely because under-invalidation bugs proved
  difficult to find and fix.

To combat these issues, this paper introduces
  a new oracle that detects under-invalidation bugs
  via \emph{self-differential testing},
  where either a large or small change results in
  the \emph{same} web page,
  and where differences thus indicate under-invalidation,
  and validate this oracle on bugs mined from
  real-world browser bug databases.
We extend this basic idea into \toolname, a fuzzer
  that uses self-differential testing to detect under-invalidation bugs
  using random generation and minimization
  of complex web pages and web page changes,
  and leveraging automated bug clustering
  to reduce the bug review burden.
We demonstrate that \toolname is effective at
  both rapidly finding under-invalidation bugs
  (\NumBugsChromeWeights in Chrome and \NumBugsFfxWeights in Firefox)
  and minimizing and clustering them,
  reducing the style-element review volume by approximately 385x.
\NumBugsNovel bugs found by \toolname
  were reported to Chrome and Firefox,
  all accepted by developers and \NumBugsFixed already fixed.
\toolname is now used as part of Mozilla's fuzzing workflow
  to find under-invalidation bugs during development.

This paper makes the following contributions:
\begin{itemize}
    \item A new class of bugs, under-invalidation bugs,
      that can be efficiently detected using \emph{self-differential} testing;
    \item \toolname, a targeted fuzzer for under-invalidation bugs
      that generates web pages and web page changes,
      detects under-invalidation bugs with self-different testing,
      and minimizes and clusters the resulting bugs to reduce review load.
    \item An evaluation of \toolname and its major components
      on both Chrome and Firefox,
      measuring bug discovery, minimization, and clustering
      with both direct and ablation studies.
\end{itemize}
\noindent
We release \toolname
  together with evaluation artifacts, test cases, and benchmarks
  at the following URL: https://anonymous.4open.science/r/lqc-7D637/.
