\documentclass[10pt,conference]{IEEEtran}

\usepackage{cite}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}

\title{Fuzzing for Web Browser Under-Invalidation Bugs}

\author{\IEEEauthorblockN{Anonymous Submission}}



\begin{document}

\maketitle

\begin{abstract}
Fuzzing for web browsers has traditionally focused on
  crash testing, such as for finding security-relevant bugs
  in parsers and media processing engines,
  and regression testing, such as for finding newly-introduced bugs
  in rendering code.
However, fuzzing has not traditionally been used
  for finding correctness bugs in the implementation
  of the web platform standards,
  because writing effective test oracles for these standards is challenging.
We introduce a new class of correctness bugs
  that afflict web browser layout engines:
  under-invalidation bugs,
  which bugs cause browsers to incompletely update
  internal state in response to user interactions.
These bugs are challenging for browser developers:
  Google Chrome rewrote their layout engine architecture
  to make under-invalidation bugs rarer,
  while Mozilla Firefox has had performance rewrites stall
  due to the difficulty of ensuring the absence of under-invalidation bugs.

To combat these bugs, we introduce LayoutQuickCheck,
  a fuzzer for finding, minimizing, and clustering
  under-invalidation bugs.
LayoutQuickCheck uses the browser as its own oracle,
  comparing an incremental and from-scratch layout
  of the same web page and flagging any differences
  as under-invalidation bugs.
LayoutQuickCheck reproduces XXX bugs
  from Chrome and Firefox's public bug trackers
  and also finds XXX novel bugs
  that are reported to and accepted by the developers,
  of which XXX have already been fixed.
Moreover, LayoutQuickCheck's minimization tooling
  is able to reduce the size of generated bugs
  from an average of XXX elements to just XXX,
  with XXX containing just a single modified CSS style,
  and its clustering algorithm is able to cluster
  XXX generated bugs into just XXX clusters,
  dramatically reducing the time needed to triage bugs.
  \begin{itemize}
\item \textbf{Chrome}
\begin{itemize}
\item 1137427 - fixed
\item 1166887 - fixed
\item 1189755 - fixed
\item 1189762 - Removed the bug from the Available Hotlist Aug 21, 2025
\item 1190220 - Fixed (Verified)
\item 1219641 - Removed the bug from the Available Hotlist Sep 17, 2025
\item 1224721 - fixed
\item 1229681 - Removed the bug from the Available Hotlist Oct 10, 2025
\end{itemize}

\item \textbf{Firefox}
\begin{itemize}
\item 1721719 - open
\item 1724982 - open
\item 1724991 - open
\item 1733276 - open
\item 1735376 - closed
\item 1735931 - closed
\item 1748891 - open
\item Metabug 1724999 - open
\end{itemize}
\end{itemize}

\end{abstract}

\section{Introduction}

\textit{Web browsers}---software that retrieves, interprets, and
displays web pages---are central to modern computing, with
browser-based usage corresponding to over \textbf{80\%} of daily work
in some organizations~\cite{montenegro2025workforce}. As web browsers
have become the primary interface for accessing the Internet, ensuring
their correctness and reliability is critical. Browser makers,
including Mozilla, Google, and Apple, thus put significant resources
behind fuzzing, audits, and security research aimed at preventing bugs
in their browsers~\cite{google-project-zero,mozilla-mythos}. Moreover,
browser developers collaborate on substantial standardization
efforts~\cite{w3c,whatwg}, share enormous test suites~\cite{wpt}, and
take part in annual ``Interoperability'' efforts to ensure that
browsers implement those standards correctly~\cite{interop}.
In short, browser developers care a lot about correctness.

Developers increasingly use \textit{fuzzing}, an automated testing
technique that exercises software with large numbers of randomly
generated or mutated inputs, to identify and fix such issues. Fuzzers
have been broadly successful in finding browser bugs as well. R2Z2,
for example, detects rendering regressions by fuzzing the output of
different browser versions~\cite{song2022r2z2}. Metamong detects
render-update bugs by fuzzing browser update behavior against a
specialized render-update check~\cite{song2023metamong}. FuzzOrigin
targets UXSS vulnerabilities through origin
fuzzing~\cite{kim2022fuzzorigin}. However, \textbf{one important
  browser mechanism remains difficult to test systematically}:
\textit{layout invalidation}, which determines which parts of a page
must be recomputed after changes to the DOM or CSS.

Unfortunately, layout invalidation is one of the most complex parts of
a browser to get right. To show a user a web page, the browser goes
through a ``rendering pipeline'' containing many steps, such as
parsing, matching, styling, layout, paint, and so on~\cite{wbe}. When
the user then interacts with the page, or when JavaScript-accessible
APIs modify it, the browser has to \emph{redo} each of those steps.
\emph{Invalidation} is the algorithm that reuses as much previous work
as possible, so that the rendering pipeline can be performed quickly.
Public browser-engine trackers reveal numerous invalidation failures
in Chromium~\cite{chromium497183437,chromium379886422},
Firefox~\cite{mozilla1452426,mozilla539356}, and WebKit-based browsers
such as Safari~\cite{webkit233421,webkit97801}. Layout engines are
often specifically designed to minimize invalidation bugs, even at the
cost of higher memory usage or lower performance. For example,
Chrome's LayoutNG~\cite{kilpatrick2021layoutng} uses a functional approach to simplify
invalidation. Some promising optimizations never ship because it is
too difficult to ensure they are bug-free, as happened to Mozilla's
reflow roots optimization~\cite{mozilla2006reflow}. In other words, invalidation
correctness is a major bottleneck on browser performance. This makes
it an especially attractive target for automated testing. However,
\textbf{web browsers layout under-invalidation remains insufficiently
  targeted} by existing fuzzing approaches.

To address these challenges and support targeted testing of browser
layout invalidation, this paper introduces LayoutQuickCheck: a fuzzer
for detecting under-invalidation bugs in modern web browser engines.
LayoutQuickCheck systematically exercises incremental layout behavior
by generating DOM and CSS updates that force the browser to recompute
affected rendering state. Central to LayoutQuickCheck is a
\emph{self-comparison strategy}: the system compares the browser's
incremental layout result against its own from-scratch layout result
for the same final page, allowing it to detect under-invalidation bugs
without relying on a separate browser implementation. This ensures
that false positives are rare, unlike cross-browser or cross-version
approaches where benign browser differences can swamp the true
detection rate. LayoutQuickCheck further uses minimization and
clustering techniques to reduce generated failures into smaller,
developer-actionable reports.

We implement LayoutQuickCheck as a browser-based fuzzing pipeline and evaluate its effectiveness across modern web browser engines, including Chrome, Firefox, and Safari. We empirically evaluate LayoutQuickCheck through experiments and ablation studies that measure how its input generation, minimization, and clustering components contribute to discovering and triaging under-invalidation bugs. Notably, LayoutQuickCheck reveals XXX previously unknown under-invalidation bugs across XXX browser engines, of which XXX are confirmed or fixed by browser developers. 

Through the following contributions, this paper introduces \textbf{the first targeted approach for uncovering under-invalidation bugs in today's browser layout engines} :

\begin{itemize}
    \item We explore the challenges of extending fuzzing to browser layout invalidation. We survey existing browser fuzzing approaches and discuss their limitations with respect to systematically detecting under-invalidation bugs.

    \item We use these insights to design LayoutQuickCheck: a targeted fuzzer for detecting under-invalidation bugs in browser layout engines. We detail how LayoutQuickCheck generates DOM and CSS updates, compares incremental and from-scratch layout results, and produces bug reports for stale layout or rendering state.

    \item We analyze LayoutQuickCheck through experiments and ablation studies across XXX browser engines. We show that LayoutQuickCheck enables effective under-invalidation bug discovery, culminating in the identification of XXX new bugs, of which XXX are confirmed or fixed by browser developers.

    \item We release LayoutQuickCheck together with our evaluation artifacts, generated test cases, and benchmarks at the following URL: XXX.
\end{itemize}


\section{BACKGROUND, RELATED WORK, AND MOTIVATION}
This section introduces the fundamental topics related to LayoutQuickCheck:
web browsers, under-invalidation bugs, and the challenges of fuzzing browser
layout engines.
\subsection{Web Browsers}
\begin{itemize}
    \item Web browsers are among the most widely used and economically important software systems, serving as the primary interface through which users access web applications, documents, media, and services. Their underlying engines require massive sustained investment: Open Web Advocacy estimates that Google alone currently provides roughly 90\% of Chromium development funding and invests around \$1 billion annually in the web platform~\cite{owa2025googleSearchMonopoly}.To implement these systems, browser vendors rely on large dedicated rendering
engines that parse web content, compute style and layout, execute scripts, and
paint pixels to the screen. Common examples include Chromium's Blink
engine~\cite{chromiumBlink}, Mozilla's Gecko engine~\cite{mozillaGecko}, and
Apple's WebKit engine~\cite{webkitEngine}.

Unlike many traditional fuzzing targets, web browsers process highly structured
documents made up of HTML elements, CSS style rules, and JavaScript updates.
Together, these inputs cause layout engines to change both page structure and
style by adding or removing elements, modifying attributes, changing inline styles,
updating stylesheet rules, or toggling classes. Even a small page can exercise
large parts of the rendering pipeline, including DOM parsing, selector matching,
style resolution, layout, and invalidation~\cite{kosaka2018insideBrowserPart3,mdnWebPerformance}.


This structure makes browser fuzzing difficult. A naive fuzzer will often produce
inputs that are syntactically invalid before reaching deep layout-engine behavior.
Effective browser fuzzing therefore requires more than just generating valid
inputs: the inputs must also be optimized toward the specific class of bugs being
tested~\cite{mozillaFuzzing,ventuzelo2023browserFuzzing,araoz2026webFuzzing}. For layout under-invalidation bugs,
this means producing pages and updates that are likely to expose incorrect
interactions among HTML structure, CSS properties, DOM mutations, and rendering updates.


After a page has been loaded, browsers rarely recompute and repaint the entire
page for every change. Instead, they use invalidation logic to decide which
parts of the rendering state are affected by a DOM or CSS update. Correct
invalidation is essential because the browser must preserve the performance
benefits of incremental rendering while still ensuring that the final pixels on
screen match the page's current state~\cite{firefoxPerformanceBestPractices,kosaka2018insideBrowserPart3}.

Invalidation mistakes generally fall into two categories. Over-invalidation
marks too much of the page as dirty, causing the browser to repeat unnecessary
style, layout, or paint work and hurting performance~\cite{mdnWebPerformance,firefoxPerformanceBestPractices}. Under-invalidation is more
dangerous for correctness: the browser updates too little, allowing stale layout
or rendering state to remain visible as incorrect pixels. Modern layout engines
therefore treat under-invalidation as a core correctness problem, and Chromium's
LayoutNG redesign explicitly emphasizes reducing these classes of layout
correctness bugs~\cite{kilpatrick2021layoutng}.
\end{itemize}
\subsection{Why Fuzzers Fail to Find Under-Invalidation Bugs}

Fuzzing has been highly effective for browser testing, but most browser fuzzers
are optimized for bug classes with more explicit failure signals. JavaScript-engine
fuzzers such as CodeAlchemist and DIE generate complex programs to expose
crashes and security vulnerabilities in JavaScript engines~\cite{han2019codealchemist,park2020die}. Other
browser fuzzers target specialized attack surfaces, such as WebGL or
WebAssembly, where crashes, memory corruption, or API errors provide concrete
oracles for failure~\cite{peng2023gleefuzz,draissi2025wemby}. These approaches
are valuable for browser security, but they do not directly test whether a
layout engine correctly updates stale rendering state after a DOM or CSS change.

Rendering-engine fuzzers begin to address this issue, but their goals still differ
from detecting under-invalidation. RTFuzz, for example, mutates render-tree
state to increase testing depth in layout and painting modules, but evaluates
success primarily through robustness defects such as crashes~\cite{zeng2026rtfuzz}. 
Differential rendering fuzzers such as R2Z2 compare outputs across browser
versions, Metamong compares different rendering executions to find render-update
bugs, and JANUS compares visual deltas across browsers to detect non-crash
rendering bugs~\cite{song2022r2z2,song2023metamong,zhou2025janus}.

These oracles are useful, but they do not fully solve layout under-invalidation:
cross-version or cross-execution differences still require determining which
result is correct, and broad visual/render-update checks are not necessarily
focused on the layout invalidation decisions triggered by specific CSS and DOM
updates. \textbf{Layout under-invalidation therefore needs a more targeted oracle.}

\subsection{Why it is Difficult to Isolate Under-Invalidation Bugs?}

In addition to detecting an under-invalidation symptom, the test case must also be 
reduced in a way that preserves the underlying bug. This is difficult because 
incremental layout behaves like a cache-like optimization: the browser tries 
to reuse previous layout results and recompute only the portions affected by 
a change~\cite{panchekha2024reusing}. As a result, a stale layout result may 
depend on a precise sequence of conditions, including the initial DOM tree, 
the initial styles, the page mutation, and the browser’s internal invalidation 
decisions about which cached layout data to reuse. If we do not carefully isolate
the sequence of page state, mutation, and layout reuse decisions that exposes the
issue, the browser may behave differently and the bug may disappear.

The complexity of layout engines also makes bug reports hard to reduce to their root 
cause. Modern layout behavior involves interacting features, dependency ordering, and 
incremental schedules that are difficult to reason about manually. 
Prior work on layout-engine synthesis observes that correct and efficient incremental 
layout requires reasoning about when recomputation can safely be skipped~\cite{liu2023medea}. 
As a result, many generated tests can expose the same underlying invalidation mistake 
through different combinations of elements, CSS properties, and mutations. Conversely, 
two tests that look similar in their HTML/CSS structure may exercise different layout dependencies.

These challenges make both minimization and deduplication necessary. A useful bug report
should remove unrelated elements, styles, and mutations while preserving the exact 
mismatch~\cite{zellerFuzzingBookReducer}. For HTML/CSS tests, reduction also needs 
to respect document structure so that minimized tests remain valid and 
meaningful~\cite{misherghi2006hdd,webkitTestCaseReduction}. LayoutQuickCheck 
therefore must minimize generated pages and group multiple reports that likely 
represent the same underlying invalidation failure, so developers are not left 
triaging many large, redundant HTML/CSS files.

\begin{center}
\fbox{
\begin{minipage}{0.95\linewidth}
\textbf{Motivation: the need for an under-invalidation browser layout fuzzer.}
As existing browser fuzzers struggle to detect layout under-invalidation bugs,
we aim to bridge the gap between browser fuzzing and incremental layout
correctness. We envision a world where browser layout invalidation is testable
just like other browser components, and thus design a fuzzer to meet these
capabilities: \textbf{LayoutQuickCheck}.
\end{minipage}
}
\end{center}

\section{CHALLENGES AND SOLUTIONS}
In order to create a system for fuzzing under-invalidation bugs, we define the main challenges that must be overcome.

\subsection{Challenge 1: Generating Inputs that Trigger Under-Invalidation Bugs}
The goal is not only to generate valid pages, but to generate page updates that are likely to exercise layout invalidation logic. Layout QuickCheck therefore biases generation toward CSS changes that should force the browser to recompute layout.
\begin{itemize}
    \item P1: \texttt{display} is a useful target because it controls major layout modes and can affect both an element and its descendants.
    
    \item P2: Grid layout creates many invalidation opportunities because templates, gaps, placement, and auto-flow can all change how children are positioned.
    
    \item P3: \texttt{display:flow-root} is important because it changes layout boundaries and reflow-root behavior.
    
    \item P4: Width and height changes directly affect box geometry, making them natural triggers for missed layout updates.
    
    \item P5: Percentage sizes exercise parent-dependent layout constraints, while pixel sizes make expected geometry changes easier to observe.
    
    \item P6: Transform changes affect visual position and reported geometry, so stale transform state can expose missed updates.
    
    \item P7: Disabling noisy properties such as \texttt{writing-mode}, \texttt{content-visibility}, padding, and table display values keeps generated tests focused on the layout behavior being studied.
    

\end{itemize}
Solution 1: The system steers random CSS updates toward properties whose changes should require layout invalidation, then checks whether incremental rendering matches a fresh layout.

\subsection{Challenge 2: Minimizing and Isolating Under-Invalidation Bugs}

Under-invalidation bugs often produce large and complex inputs that are difficult to analyze.

\begin{itemize}
    \item P1: Effective bug trigering inputs are very large.
    
    \item P2: Large HTML and CSS inputs make bug isolation difficult.
    
    \item P3: Minimization techniques are expensive and time consuming.
\end{itemize}

Solution 2: The system minimizes bug-triggering inputs and extracts the core structures responsible for the bug.
\subsection{Challenge 3: Grouping and Categorizing Under-Invalidation Bugs}

A major challenge in layout fuzzing is reducing duplicate bug reports.

\begin{itemize}
    \item P1: Fuzzers often generate many inputs that trigger the same underlying bug.
    
    \item P2: Identifying the core structure of a bug is difficult, especially when the process must be automated.
    
    \item P3: Structural and style relationships must be represented consistently.

    \item P4: Some invalidation bugs require architectural changes, so reports should help developers focus on identifying recurring and fixable patterns.
\end{itemize}

Solution 3: The system groups bugs using structural rules and merged bug representations so developers do not need to inspect many duplicate micro bugs and can instead focus on actionable bug patterns.

\section{IMPLEMENTATION}
Layout QuickCheck is implemented as a Selenium-based fuzzing pipeline that generates HTML/CSS test cases, runs them in a target browser, detects under-invalidation bugs, and post-processes bug reports.

\subsection{Fuzzing Process Execution}
\begin{itemize}
    \item P1: Layout QuickCheck generates a random DOM tree with base CSS styles and modified CSS styles.
    \item P2: The generated page is executed in a real browser through Selenium WebDriver.
    \item P3: The harness compares layout after incremental style changes against layout after a fresh reload to detect under-invalidation bugs.
\end{itemize}

\subsection{Test Case Mutation and Trimming}
\begin{itemize}
    \item P1: When a bug is found, Layout QuickCheck repeatedly applies minimization steps and keeps only changes that still reproduce the bug.
    \item P2: The minimizer removes unnecessary elements, CSS rules, and style changes from the generated test case.
    \item P3: \texttt{Minify\_MoveStyleChangeToFirstLoad} moves nonessential modified styles into the base styles, leaving the modified styles most critical to reproducing the bug.
    \item P4: The final minimized page is saved with metadata describing the affected styles and layout differences.
\end{itemize}
\subsection{Bug Categorization and Deduplication}
\begin{itemize}
    \item P1: Layout QuickCheck converts minimized bugs into structural representations that include the DOM tree, base styles, and modified styles.
    \item P2: The system compares new bugs against existing bug groups to identify repeated instances of the same underlying issue.
    \item P3: Matching bugs are placed into existing groups, while new patterns can form new bug groups with generated rules.
\end{itemize}
\subsection{Supported Software and Browser Platforms}
\begin{itemize}
    \item P1: Layout QuickCheck supports browser testing through Selenium variants for Chrome, Firefox, and Safari.
    \item P2: Browser variants can be configured with custom binaries, WebDriver paths, viewport sizes, and headless execution.
    \item P3: Bug reports are grouped using structural rules so repeated instances of the same underlying bug can be categorized together.
\end{itemize}

\section{EVALUATION}
(what are the concrete experiments that we want to run?Add in modified and base styles? For example for the minimization, initial vs final. Minimization with vs without the move modified styles to base styles.)

\textbf{Q1: How effective is the system at discovering under-invalidation bugs?}
Main Goal: How effective at triggering a bug?(Success rate; bugs per number of generation)
Test: Run the system for a fixed number of iterations and measure how many bugs are found.
Variance: Display property, Grid Property, Pixel vs percentage, Transform Property, Flow-root property, etc.

\vspace{0.5em}

\textbf{Q2: How effective are the minimization and clustering techniques?}

Main Goal: How effective at processing a bug?(Speed; number of iterations; time to minimize; time to cluster)
Test: Run the system for a fixed number of time units and measure how many bugs are found.
Variance: with vs without clustering; with vs without minimization; with vs without moving modified styles to base styles.

\vspace{0.5em}

\textbf{Q3: Does the system discover real and unique under-invalidation bugs?}
Main Goal: How effective at finding unique bugs?(Quality; number of unique bugs; number of duplicate bugs)
Test: Run the system for a long time and manually measure how many unique bugs are found.
Variance: ???
\vspace{0.5em}

\textbf{Benchmarks:}

\vspace{0.5em}

\textbf{Experiment Setup \& Infrastructure:}

\vspace{0.5em}

\textbf{Post-processing Results:}

\vspace{0.5em}

\subsection{Q1: How effective is the system at discovering under-invalidation bugs?}

\textbf{Outcomes:}

\vspace{0.5em}

\subsection{Q2: How effective are the minimization and clustering techniques?}

\textbf{Outcomes:}

\vspace{0.5em}

\subsection{Q3: Does the system discover real and unique under-invalidation bugs?}

\textbf{Outcomes:}

\vspace{0.5em}

\textbf{Case Study 1:}

\vspace{0.5em}

\textbf{Case Study 2:}

\vspace{0.5em}

\textbf{Case Study 3:}

\vspace{0.5em}

\textbf{Developer Responses:}

\vspace{0.5em}

\section{DISCUSSION \& THREATS TO VALIDITY}

\textbf{Improving Runtime Throughput:}

\vspace{0.5em}

\textbf{Supporting Other Browsers:}

\vspace{0.5em}

\textbf{(Other limitation 1)}

\vspace{0.5em}

\textbf{(Other limitation 2)}

\vspace{0.5em}

\section{CONCLUSION}

\section*{ACKNOWLEDGMENTS}

\nocite{kilpatrick2021layoutng,panchekha2024reusing,mozilla2006reflow}
\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
